A Survey on Ordered Binary Decision Diagrams

### 2015-09-10 paper.tex
Add workaround to get line break after paragraph
Reformat
Add figures and references

\begin{figure}[ht]
    \centering
    \subfigure[BDD]{
        \includestandalone[height = 3cm]{figs/bdd}
        \label{fig:bdd}
    }
    \hskip1cm
    \subfigure[OBDD]{
        \includestandalone[height = 3cm]{figs/obdd}
        \label{fig:obdd}
    }
    \caption{BDD and OBDD of $f=(A \land B) \lor (B \land C)$.}
\end{figure}

@@

\paragraph*{Reduction procedure}

@@

The third and thus last transformation rule deals with completely redundant 
nonterminal nodes. Intuitively, this rule should be straightforward: any node
having the same child on all outgoing edges is redundant because the actual value
of the variable does not change the result of the function. More formally, a
nonterminal node $n$ is redundant if $lo(n) = hi(n)$. Then, all incoming edges
of $n$ can be redirected to $lo(n)$ and $n$ can be deleted afterwards.

\tbr

>>>>

\begin{figure}[ht]
    \centering
    \subfigure[BDD]{
        \includestandalone[height = 3cm]{figs/bdd}
        \label{fig:bdd}
    }
    \hskip1cm
    \subfigure[OBDD]{
        \includestandalone[height = 3cm]{figs/obdd}
        \label{fig:obdd}
    }
    \label{fig:bdd-and-obdd}
    \caption{BDD and OBDD of $f=(A \land B) \lor (B \land C)$.}
\end{figure}

@@

\paragraph*{Reduction procedure}
\mbox{} % workaround to get line break after paragraph

@@

The third and last transformation rule deals with completely redundant nonterminal
nodes. Intuitively, this rule should be straightforward: any node having the same
child on all outgoing edges is redundant because the actual value of the variable
does not change the result of the function. More formally, a nonterminal node $n$
is redundant if and only if $lo(n) = hi(n)$. Then, all incoming edges of $n$ can
be redirected to $lo(n)$ and $n$ can be deleted afterwards.

\begin{figure}[ht]
    \centering
    \subfigure[]{
        \includestandalone[height = 3cm]{figs/redundant-nonterminals-before}
        \label{fig:redundant-nonterminals-before}
    }
    \hskip1cm
    \subfigure[]{
        \includestandalone[height = 3cm]{figs/redundant-nonterminals-after}
        \label{fig:redundant-nonterminals-after}
    }
    \label{fig:redundant-nonterminals}
    \caption{Eliminating redundant nonterminal nodes.}
\end{figure}

Figure~\ref{fig:obdd} shows the result of applying the first two transformation
rules to the BDD shown in Figure~\ref{fig:bdd}. The third rule is shown
in Figure~\ref{fig:redundant-nonterminals}.
Figure~\ref{fig:redundant-nonterminals-before} shows a BDD with redundant
nonterminal nodes (both \textbf{B}'s, in essence) and
Figure~\ref{fig:redundant-nonterminals-after} shows the equivalent OBDD without
redundant nonterminals. \tbr
